\documentclass{article}
\usepackage{titlesec}
\usepackage{amsmath}

\title{HW2}
\author{212783187}
\renewcommand\thesection{\arabic{section}.}
\renewcommand\thesubsection{\thesection \arabic{subsection}}
\begin{document}
\maketitle{}
\newpage
\section{Improved Greedy}
\subsection{}
Let's define the search problem (S, O, I, G):
\begin{itemize}
\item[S]: The two robots, where each robot is defined by (position on board, battery,  credit, current package, step).\\\\
Two packages, where each package is defined by (pickup location,  destination location).\\\\
Two charging stations, where each charging station is defined by (position on board).\\\\
Maximum step count, defined by a number (maximum step count).\\\\
Variables:
\begin{itemize}
\item position on board: 5x5 tuple. The position on a 5x5 board.
\item batery: Integer. Battery level of the robot.
\item credit: Integer. The robots' credits.
\item current package: package object. current package that the robot carries. If the robot is not carrying a package then it's set to None.
\item pickup location: 5x5 tuple. The pickup location of a package.
\item destination location: 5x5 tuple. The destination location of a package.
\item maximum step count: The maximum steps a robot can make.
\end{itemize}
\item[O]:
$$O = \{\text{move north, move south, move east, move west, pick up, drop off, charge}\}$$
\item[I]:
The initial state depends on the specific board. But we do know that in the initial state both robots are not carrying a package, and have a full battery.
\item[G]:
The game terminates when any of the following conditions hold:
\begin{enumerate}
\item The battery level of at least one robot reaches zero.
\item The maximum step count is reached.
\end{enumerate}
\end{itemize}
\subsection{}
The heuristic we implemented priorotises reaching the nearest package and delivering it. If the robot can't get more credit and the oponent picked a package, it tries to sit in the destination of that package so the oponent can't deliver the package. 
$$h = robot.battery + 4\times robot.credit$$
$$h += \left\{ \begin{array}{ll}
nearest\_package\_delivery\_dist -  nearest\_package\_dist,& robot.package = None\\
credit\_gained\_from\_delivery - dteps\_to\_delivery,& else
\end{array}\right.$$
$$h += 1000 \times (10 - opponent\_package\_destination),  if\ cant\_get\_credit\ and\ opponent.package$$
\subsection{}
The main drawback of the algorithm in comparrison with minimax is that it only looks one step into the future.  It doesn't take into account the opponent's move.
\newpage
\section{RB-Minimax}
\subsection{}
In RB-minimax we encounter a tradeoff between using resources to calculate a better heuristic, and searching deeper in the tree.\\\\
A better heuristic allows us to make a better decision based on the information we got. But the deeper we get in the search tree the more information we have, which helps the heuristic perform better.\\\\
Therefore, the advantages and disadvantages of using an easier to calculate heuristic, given the harder to calculate heuristic is more informed, are:
\begin{itemize}
\item Advantages: Can get deeper in the search tree. The deeper we get in the search tree, the more information we have which helps the heuristic make a better decision.
\item Disadvantages: Makes a worst evaluation of a given state. It could be that evaluating a deeper node, would give a worst evaluation of the current state than if we used the more informed heuristic on a shallower node.
\end{itemize}
\end{document}